### 2015-12-11 paper/2-background.tex
Proofread section 2.1

\subsection{Conservative Synchronization}
The first synchronization protocol that we will introduce, is \textit{conservative synchronization}~\cite{FujimotoBook}.
In conservative synchronization, a node is allowed to progress in simulated time, independent of all other nodes, up to the point where it can guarantee that no causality errors can happen.
When this point in time is reached, the node has to block until it is allowed to progress any further.
In practice, this means that all nodes need to be aware of the current simulation time of all other nodes, and the time it takes an event to propagate (called \textit{lookahead}).
Several algorithms are defined in the literature to implement this behaviour.
An overview is given in~\cite{FujimotoBook}.

Deadlock can occur when a dependency cycle occurs and the amount of exchanged messages is low.
Multiple algorithms are defined to handle this situation, such as deadlock avoidance and deadlock recovery.

The main advantage of conservative synchronization is that it has a low overhead if high parallelism exists between nodes.
Each node can simulate in parallel, while sporadically notifying other nodes that they can progress even further.
The disadvantage, however, is that the amount of parallelism is explicitly limited by the size of the lookahead.
If a node can influence another (almost) instantaneously, no matter how rarely it occurs, the amount of parallelism is severely reduced.
It is also up to the user to define the size of the lookahead, depending on how the model is known to behave.
Slight changes in model behaviour can cause significant changes to the lookahead, and can therefore also have a significant influence on simulation performance.

>>>>

\subsection{Conservative Synchronization}
The first synchronization protocol we introduce is \textit{conservative synchronization}~\cite{FujimotoBook}.
In conservative synchronization, a node progresses independent of all other nodes, up to the point in time where it can guarantee that no causality errors happen.
When simulation reaches this point, the node blocks until it can guarantee a new time until which no causality errors happen.
In practice, this means that all nodes are aware of the current simulation time of all other nodes, and the time it takes an event to propagate (called \textit{lookahead}).
Deadlocks can occur due to a dependency cycle of models.
Multiple algorithms are defined in the literature to handle both the core protocol, as well as resolution schemes to handle or avoid the deadlocks~\cite{FujimotoBook}.

The main advantage of conservative synchronization is its low overhead if the lookahead is high.
Each node then simulates in parallel, and sporadically notifies other nodes about its local simulation time.
The disadvantage, however, is that the amount of parallelism is explicitly limited by the lookahead.
If a node can influence another (almost) instantaneously, no matter how rarely it occurs, the amount of parallelism is severely reduced.
The user is required to define the lookahead, using knowledge about the model's behaviour.
Defining lookahead is not always a trivial task if there is no detailed knowledge of the model.
Even slight changes in the model can change to the lookahead, and can therefore have a significant influence on simulation performance.
